Constraint Grammar as a SAT problem

### 2015-06-01 paper/nodalida2015.tex
fix hyperref

\documentclass[11pt]{article}
\usepackage{nodalida2015}
\usepackage{times}
\usepackage{mathptmx}
\usepackage{fixltx2e}
%\usepackage{txfonts}
\usepackage{url}
\usepackage{latexsym}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{authordate1-4}
\usepackage{multirow}
\special{papersize=210mm,297mm} % to avoid having to use "-t a4" with dvips 
%\setlength\titlebox{6.5cm}  % You can expand the title box if you really have to

@@

\section{Applications}
\label{sec:apps}
As demonstrated in Section~\ref{sec:eval}, our implementation is not
competitive with the state of the art. It is more fruitful to focus on
things where the SAT-based representation can make an impact.
One such thing is grammar analysis\footnote{We thank Eckhard Bick for
  the suggestion.}.
There has been work on automatic tuning of hand-written CGs
\cite{bick2013tuning}, but to our knowledge, no tools which would
search for inconsistencies or unoptimal design in order to point it out to the grammar writer.

@@

As future work, we intend to test for conflicts
without using a corpus.
Let us illustrate the idea with the same two rules,
\texttt{SELECT v} and \texttt{REMOVE v IF (-1 det)}
in both orders.
Assume we have the tag set \texttt{\{det, n, v\}}, 
and we want to find if there exists an input such that
 both rules, applied in the given order, remove something from the input.
% This is another constraint solving problem, hence we can model it in SAT.
There are no inputs that satisfy the requirement with the first order,
but several that work with the second, such as the following:

>>>>

\documentclass[11pt]{article}
\usepackage{nodalida2015}
\usepackage{times}
\usepackage{mathptmx}
\usepackage{fixltx2e}
%\usepackage{txfonts}
\usepackage{url}
\usepackage{latexsym}
\usepackage{cite}
\usepackage[colorlinks=true]{hyperref}
\usepackage{authordate1-4}
\usepackage{multirow}
\special{papersize=210mm,297mm} % to avoid having to use "-t a4" with dvips 
%\setlength\titlebox{6.5cm}  % You can expand the title box if you really have to

@@

\section{Applications and future work}
\label{sec:apps}
%As demonstrated in Section~\ref{sec:eval}, our implementation is not
%competitive with the state of the art. 
%VISL CG-3 is efficient, reliable and widely used, and
Instead of trying to compete with the state of the art, we plan to use SAT-CG for grammar analysis\footnote{We thank Eckhard Bick for the idea.}.
There has been work on automatic tuning of hand-written CGs
\cite{bick2013tuning}, but to our knowledge no tools which would
search for inconsistencies or unoptimal design. %in order to point it out to the grammar writer.

@@

Finally, we intend to test for conflicts
without using a corpus.
Let us illustrate the idea with the same two rules,
\texttt{SELECT v} and \texttt{REMOVE v IF (-1 det)}
in both orders.
Assume we have the tag set \texttt{\{det, n, v\}}, 
and we want to find if there exists an input such that
 both rules, applied in the given order, remove something from the input.
% This is another constraint solving problem, hence we can model it in SAT.
There are no inputs that satisfy the requirement with the first order,
but several that work with the second, such as the following:
